Synthesizing Symmetric Lenses

### 2018-07-12 papers/SymmetricLenses/main.tex
ah

Having determined appropriate examples and timing parameters for the 48
benchmarks, we evaluate the performance of the system by 
measuring the running time of our algorithm in two modes:

>>>>

Having determined appropriate examples and termination parameters for the 48
benchmarks, we evaluate the performance of the system by measuring the running
time of our algorithm in two modes:
